Compositional Certified Resource Bounds

### 2014-06-30 paper/main.tex
add last examples

\begin{figure*}[t!]
 \setlength{\progwidth}{.24\linewidth}
  \centering
%
%
  \begin{minipage}[b]{\progwidth}
    \begin{center}
   \begin{lstlisting}
 XXX
   \end{lstlisting}

$XXX$
\\[.7\baselineskip]
      {\bf Knuth-Morris-Pratt}
    \end{center}
  \end{minipage}
%
%
  \begin{minipage}[b]{\progwidth}
    \begin{center}
   \begin{lstlisting}
 XXX
   \end{lstlisting}

$XXX$
\\[.7\baselineskip]
      {\bf Greatest Common Divisor}
    \end{center}
  \end{minipage}
%
%
  \begin{minipage}[b]{\progwidth}
    \begin{center}
   \begin{lstlisting}
 XXX
   \end{lstlisting}

$XXX$
\\[.7\baselineskip]
      {\bf Quick Sort}
    \end{center}
  \end{minipage}

>>>>

\begin{figure*}[t!]
 \setlength{\progwidth}{.32\linewidth}
  \centering
%
%
  \begin{minipage}[b]{\progwidth}
    \begin{center}
   \begin{lstlisting}
int srch(
  int t[], int n,
  int p[], int m,
  int b[]
) {
  int i=0, j=0, k=-1;

  while (i < n) {
    while (j >= 0 && t[i]!=p[j]) {
      k = b[j];
      assert(k > 0);
      assert(k <= j + 1);
      j -= k;
    }
    i++, j++;
    if (j == m)
      break;
  }
  return i;
}
   \end{lstlisting}

$1 + 2|\inter 0 n|$
\\[.7\baselineskip]
      {\bf Knuth-Morris-Pratt}
    \end{center}
  \end{minipage}
%
%
  \begin{minipage}[b]{\progwidth}
    \begin{center}
   \begin{lstlisting}
int gcd(int x, int y) {
  if (x <= 0) return y;
  if (y <= 0) return x;

  for (;;) {
    if (x>y) x -= y;
    else if (y>x) y -= x;
    else return x;
  }
}
   \end{lstlisting}

$|\inter 0 x| + |\inter 0 y|$
\\[.7\baselineskip]
      {\bf Greatest Common Divisor}
    \end{center}
  \end{minipage}
%
%
  \begin{minipage}[b]{\progwidth}
    \begin{center}
   \begin{lstlisting}
void qsort(int a[], int lo, int hi) {
  int m1, m2, n;

  if (hi - lo < 1) return;

  n = nondet(); /* partition the array */
  assert( n > 0 );
  assert( lo + n <= hi );

  m1 = n + lo;
  m2 = m1 - 1;

  qsort(a, m1, hi);
  qsort(a, lo, m2);
}

void main(int a[], int len) {
  qsort(a, 0, len);
}
   \end{lstlisting}

$1 + 2 |\inter 0 {\code{len}}|$
\\[.7\baselineskip]
      {\bf Quick Sort}
    \end{center}
  \end{minipage}
